RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-28 casestudies.tex
whatever
update
section ids
figure and case studies and discussion

% IMPORTANT: what is unique about RCloud here

% From prototyping to dashboard

% Getting other information from the web

%

>>>>

\subsection{stock tickers\ref{sec:stockvis}}

Basic stock ticker visualization via ggplot by Hadley Wickham.

Easy to convert it into configurable entry point for dashboarding.

Now consider an analyst that wants to understand the price dynamics of
different stock attributes, different points in time, etc. For that,
interactive visualization is very attractive. describe dcplot and
notebook which uses it.

Then describe abstraction of stock-data fetching, to talk about
calling notebooks from other notebooks.

then call.r?

\subsection{text analysis\ref{sec:textvis}}

Same.

% IMPORTANT: what is unique about RCloud here
% From prototyping to dashboard
% Getting other information from the web
%
